% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=397249]
\definecolor[rulecolor][h=9cb770]

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=10mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt, helvetica]

\setupwhitespace[medium]

\setupblackrules[width=31mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[raziyeh-bazargan]{Raziyeh Bazargan}

\thinrule

\subsubsubsubsection[bellevue-wa-425-598-5126-raziyeh.bazargangmail.com]{Bellevue,
WA \letterbar{} (425) 598-5126 \letterbar{} Raziyeh.bazargan@gmail.com}

\thinrule

\subsection[summary]{Summary}

Junior Web Developer specializing in front end development. Experienced
with all stages of the development cycle for dynamic web projects.

Highly self-motivated and results- driven, fast learner, strong team
player, interacting and collaborating with coworkers at all levels and
strong problem solving and analytical abilities with solid documentation
tendencies.

Understanding of relational databases with experience in SQL Server.
Client-side web development skills on HTML, CSS, JavaScript, jQuery,
Bootstrap and AngularJs.

\thinrule

\subsection[experience]{Experience}

{\bf {\em Feb 2015 - Jun 2016}}

{\bf Web Developer,
\useURL[url1][http://pingle.co][][Pingle]\from[url1], Seattle, WA.}

\startitemize
\item
  Design responsive layouts for new website clients using:
  {\bf {\em Javascript}}, {\bf {\em Bootstrap}}, {\bf {\em HTML}},
  {\bf {\em CSS}}.
\item
  Develop new user-facing features.
\item
  Assure that all user input is validated before submitting to back-end.
\item
  Fix bugs and implement new features from the database to the views
  using: {\bf {\em C\#}}, {\bf {\em Typescript}}, {\bf {\em AngularJS}}
  and {\bf {\em SQL server}}.
\item
  Working with Visual studio online and Team Foundation Version Control
  {\bf (TFVC)}.
\stopitemize

{\bf {\em Feb 2015 - Jun 2016}}

{\bf Software Specialist, \useURL[url2][http://rahyab.ir][][Rahyab
Gayaneh Gostar]\from[url2], IRAN.}

\startitemize
\item
  Gathered and analyzed customers change requests and created related
  ticket for development team.
\item
  Found the root cause for every issue, assigning it to the appropriate
  developer.
\item
  Identified problems based on the users reports.
\item
  Supporting Company Products.
\item
  Analyzing new software requests from users, test, installation,
  support and maintenance.
\stopitemize

\thinrule

\subsection[education]{Education}

{\bf Front end web development}, CodeFellows, Seattle,WA

Using: HTML , CSS , JavaScript , jQuery to create fully-functional web
apps, asynchronous programming (AJAX) and database manipulation.

\startitemize[packed]
\item
  {\em Related Projects:}
  \useURL[url3][http://ractrac.herokuapp.com/][][Racktrack]\from[url3]
  and \useURL[url4][http://baby-safe.herokuapp.com/][][Baby
  Safe]\from[url4]
\stopitemize

{\bf Bachelor's degree}, Software Engineering, Islamic Azad University,
Iran.

{\bf Associate's degree}, Software Engineering, Fatemiyeh Junior
College, Iran.

\thinrule

\subsection[skills-strengths]{Skills & Strengths}

\startitemize
\item
  {\bf Web Development} : HTML, CSS, Bootstrap, JavaScript, jQuery,
  AngularJS.
\item
  {\bf Web Tools} : Grunt, Bower.
\item
  {\bf Programming Languages} : C\# (beginner) , Typescript
\item
  {\bf DataBase} : SQL Server
\item
  {\bf Source Control} : GitHub, TFVC
\stopitemize

\thinrule

\subsection[languages]{Languages}

\startitemize[packed]
\item
  Persian (Native)
\item
  English
\stopitemize

\thinrule

\startblockquote
\useURL[url5][https://github.com/Raziyehbazargan][][GitHub]\from[url5]
\letterbar{}
\useURL[url6][https://www.linkedin.com/in/raziyehbazargan][][Linkedin]\from[url6]
\letterbar{} \useURL[url7][http:raziyeh.info][][Portfolio]\from[url7]
\stopblockquote

\stoptext
